Report and Figures

### 2016-11-12 figs.Rmd
modified legends in cluster map

races <- c('Asian', 'Black', 'Hispanic', 'Other', 'White')
city <- 'Atlanta'

@@

  g <- tracts %>% fortify(region = 'GEOID') %>% 
      tbl_df() %>% 
      left_join(df, by = c('id' = 'GEOID')) %>% 
      ggplot() + 
      geom_polygon(aes(x = long, y = lat, fill = prominent_race, group = group, alpha = prominence))  +
      ggthemes::theme_map() + 
      scale_fill_brewer(palette = 'Set1') + 
      scale_alpha_continuous(guide = 'none', limits = c(0,1)) + 
      ggtitle(city) + 
      theme(text=element_text(size=16),
            plot.title = element_text(size=20, vjust = -5),
            legend.title = element_blank(),
            legend.position="bottom")
  g
}

@@

  		g <- g + geom_polygon(aes(x = long, y = lat, group = group),data = overlay,
  		                      alpha = 0, fill = NA, size = 5*weight, color = 'black') 
    }

@@

  tracts@data$cluster <- 1
  overlay <- unionSpatialPolygons(tracts, IDs = tracts@data$cluster) %>% fortify()
  g <- g + geom_polygon(aes(x = long, y = lat, group = group),data = overlay,
  		                      alpha = 0, fill = NA, size = 5*max_weight, color = 'white')

@@

@@

```{r}
city <- 'Detroit'
print(city)
nclusters <- 1:6
g <- prominence_map(city, races)
g <- g %>% cluster_map(city, races, nclusters)

@@

@@

@@

@@

  out_dir <- paste0('figs/cluster_map_', city, '.pdf')
  ggsave(out_dir, width = 14, height = 14, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)
}
```

>>>>

races <- c('Asian', 'Black', 'Hispanic', 'Other', 'White')

@@

  g <- tracts %>% fortify(region = 'GEOID') %>% 
      tbl_df() %>% 
      left_join(df, by = c('id' = 'GEOID')) %>% 
      ggplot() + 
      geom_polygon(aes(x = long, y = lat, fill = prominent_race, group = group, alpha = prominence))  +
      ggthemes::theme_map() + 
      scale_alpha_continuous(guide = 'none', limits = c(0,1)) + 
      ggtitle(city) + 
      theme(plot.title = element_text(size=20, vjust = -5),
            legend.title = element_blank(),
            legend.position = c(.7, .1))
  g
}

@@

  		g <- g + geom_polygon(aes(x = long, y = lat, group = group),data = overlay,
  		                      alpha = 0, fill = NA, size = 8*weight, color = 'black') 
    }

@@

  tracts@data$cluster <- 1
  overlay <- unionSpatialPolygons(tracts, IDs = tracts@data$cluster) %>% fortify()
  g <- g + geom_polygon(aes(x = long, y = lat, group = group),data = overlay,
  		                      alpha = 0, fill = NA, size = 8*max_weight, color = 'white')

@@

  g <- prominence_map(city, races)
  g <- g + scale_fill_brewer(palette = 'Set1')

@@

```{r}
city <- 'Detroit'
print(city)
nclusters <- 1:6
g <- prominence_map(city, races)

guide <- guide_legend(label.theme = element_text(size = 14, angle = 0))

g <- g + scale_fill_brewer(palette = 'Set1', guide = guide)

g <- g %>% cluster_map(city, races, nclusters)

@@

ggsave(out_dir, width = 14, height = 10, units = 'cm')
embed_fonts(out_dir, outfile=out_dir)

```
```{r}

g <- g + scale_fill_brewer(palette = 'Set1', guide = guide)
g + theme(legend.position = c(.8, .1))

@@

  if(city %in% c('Detroit', 'Philadelphia')){
    guide <- guide_legend(label.theme = element_text(size = 14, angle = 0))

  }else{
    guide = FALSE
  }

  g <- g + scale_fill_brewer(palette = 'Set1', guide = guide)

@@

  ggsave(out_dir, width = 14, height = 10, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)

@@

  out_dir <- paste0('figs/cluster_map_', city, '.pdf')
  ggsave(out_dir, width = 14, height = 10, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)
}
```
